MSAD_PCA_Walkthrough

### 2017-02-02 README.Rmd
Example added to README. Documentation first round complete.

## Examples

>>>>

## Examples
These are the examples shown in the help files for hte mspTrain(), mspMonitor(), and mspWarning() functions.
```{r mspExamples}
data("normal_switch_xts")
# The state values are recorded in the first column.
n <- nrow(normal_switch_xts)
nTrainObs <- floor(0.4 * n)

# Calculate the training summary, but save five observations for monitoring.
trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
                            labelVector = normal_switch_xts[1:(n - 5), 1],
                            trainObs = nTrainObs,
                            lagsIncluded = 1)

trainResults_ls

# While training, we included 1 lag (the default), so we will also lag the
# observations we will test.
testObs <- normal_switch_xts[(n - 6):n, -1]
testObs <- stats::lag(testObs, 0:1)
testObs <- testObs[-1, ]
testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
testObs

# Run the monitoring function.
dataAndFlags <- mspMonitor(observations = testObs[, -1],
                           labelVector = testObs[, 1],
                           trainingSummary = trainResults_ls$TrainingSpecs)

dataAndFlags

# Alarm check the last row of the matrix returned by the mspMonitor function
mspWarning(dataAndFlags)
```
